---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Models {#runmodels}

## Part 1: Combine Data  
```{r load combined data}
loadRData <- function(fileName, type){
#loads an RData file, and returns it
    path <- sprintf("%s/data/clean/%s_cleaned.RData", wd, fileName)
    load(path)
    get(ls()[grepl(type, ls())])
}

# which(apply(nested_data %>% mutate(cols = map(data, colnames)) %>% select(-data) %>% unnest(cols) %>% mutate(inc = "yes") %>% spread(study, inc), 1, function(x){sum(is.na(x))/7*100}) < 25)

nested_data <- tibble(
  study = studies
  , data = map(str_to_lower(study), ~loadRData(., "combined"))
) %>%
  mutate(
    data = map(data, ~(.) %>% 
                 ungroup() %>% 
                 mutate(SID = as.character(SID)) %>%
                 select(SID, Trait, p_year, p_value, Outcome, o_year, o_value # core variables
                        , one_of(c("age", "gender", "education", "cognition"
                                 , "alcohol", "smokes", "BMI", "race", "SRhealth"
                                 , "stroke", "cancer", "diabetes", "heartProb")))
               )
    , study = mapvalues(study, studies, studies_long)
    ) %>%
  unnest(data) %>% 
  # removing this outcome because there was no variance for WUSM MAP
  filter(!(Outcome == "vsclrInfrcts" & study == "ADRC"))
```

## Part 2: Clean and Prepare Data Sets  

### POMP and Factor Levels  
The first thing we'll do is get everything on the same scale. To do so, and as we preregistered, we will convert:
- age to centered at 60  
- education (in years) to centered at 12 years  
- personality characteristics and cognition to POMP  
- chronic conditions to 0 = no, 1 = yes
- Dementia diagnosis to 0 = no, 1 = yes
- Lewy Body Disease  (binary; 0 = none, 1 = yes, collapsing across types)  
- Gross Cerebral Infarcts, Gross Cerebral Microinfarcts, Hippocampal Sclerosis (binary; 0 = No, 1 = Yes)  

All other indicators have scales that are already standardized across studies (e.g., BMI, Braak stage, CERAD) and will not be transformed.  

```{r}
cln <- c("Study", "E", "A", "C", "N", "O", "Crystallized / Knowledge", "Age (Years)", "Education (Years)", "% Women")
fctr_vars <- c("dementia", "hipSclerosis", "lewyBodyDis", "tdp43", "vsclrInfrcts", "vsclrMcrInfrcts", "gender"
               , "smokes", "alcohol", "race", "stroke", "cancer", "diabetes", "heartProb")

transpose_df <- function(df) {
  t_df <- data.table::transpose(df)
  colnames(t_df) <- rownames(df)
  rownames(t_df) <- colnames(df)
  t_df <- t_df %>%
    tibble::rownames_to_column(.data = .) %>%
    tibble::as_tibble(.) %>%
    filter(row_number() != 1) %>% 
    set_names(c("Variable", df$study))
  return(t_df)
}



desc_tab_lat <- nested_data %>%
  select(-p_year, -o_year, -one_of(fctr_vars)) %>%
  group_by(study, Trait, Outcome) %>%
  mutate_at(vars(p_value, SRhealth), 
            ~((. - min(., na.rm = T))/(max(., na.rm = T) - min(., na.rm = T))*10)) %>%
  mutate_at(vars(p_value, SRhealth),  ~ifelse(is.infinite(.), NA, .)) %>%
  ungroup() %>%
  pivot_wider(names_from = Outcome, values_from = o_value, values_fn = mean) %>%
  pivot_wider(names_from = Trait, values_from = p_value, values_fn = mean) %>%
  group_by(study) %>% 
  mutate(n = n()) %>%
  select(-one_of(fctr_vars)) %>%
  distinct() %>%
  pivot_longer(cols = c(-study, -SID, -n), values_to = "value", names_to = "item", values_drop_na = T) %>%
  group_by(study, item, n) %>%
  summarize(est = sprintf("\\makecell{%.2f \\\\ {%.2f}}", mean(value, na.rm = T), sd(value, na.rm = T))) %>%
  ungroup() %>%
  pivot_wider(names_from = item, values_from = est) %>%
  full_join(
    nested_data %>% 
      group_by(Outcome, SID, study) %>%
      filter(o_year == min(o_year)) %>%
      ungroup() %>%
      select(-o_year) %>%
      pivot_wider(names_from = Outcome, values_from = o_value, values_fn = mean) %>%
      select(-Trait, -p_year, -p_value) %>% 
      distinct() %>%
      select(study, SID, one_of(fctr_vars)) %>% 
      distinct()  %>% 
      group_by(study) %>% 
      summarize_at(vars(-SID), ~mean(., na.rm = T)*100) %>% 
      mutate_at(vars(-study), ~ifelse(is.nan(.) | is.na(.), "", sprintf("%.2f%%", .))) %>%
      ungroup()
    ) %>%
    select(study, n, E, A, C, N, O, PA, `NA`, SWL, one_of(outcomes$short_name), 
           age, gender, education, cognition, BMI, SRhealth, smokes, alcohol, 
           BMI, race, stroke, cancer, diabetes, heartProb) %>% 
    transpose_df() %>%
  mutate(Variable = ifelse(Variable == "n", "Valid N", Variable))
  # kable(., "latex"
  #       , digits = 2
  #       # , col.names = cln
  #       , booktabs = T
  #       , caption = "Descriptive Statistics of All Harmonized Measures Across Samples"
  #       , align = c("l", rep("c",9))) %>%
  #   kable_styling(full_width = F, latex_options = c("repeat_header", "scale_down")) %>%
  #   kableExtra::group_rows("Big Five Personality", 2, 6) %>%
  #   kableExtra::group_rows("Subjective Well-Being", 7, 9) %>%
  #   kableExtra::group_rows("Dementia and Neuropathology", 10, 19) %>%
  #   kableExtra::group_rows("Covariates", 20, 32) #%>%
  # add_footnote(notation = "none", label = "\\textit{Note.} E = Extraversion; A = Agreeableness; C = Conscientiousness; N = Neuroticism; O = Openness, PA = Positive Affect, NA = Negative Affect, SWL = Satisfaction with Life; Age, education, gender, smoking, alcohol, BMI, chronic conditions, and cognition were assessed at the first baseline personality assessment.", escape = F, threeparttable = T)
save(desc_tab_lat, file = sprintf("%s/results/tables/tab-3-desc.RData", wd))

desc_tab <-
  nested_data %>%
  select(-p_year, -o_year, -one_of(fctr_vars)) %>%
  group_by(study, Trait, Outcome) %>%
  mutate_at(vars(p_value, SRhealth), 
            ~((. - min(., na.rm = T))/(max(., na.rm = T) - min(., na.rm = T))*10)) %>%
  mutate_at(vars(p_value, SRhealth),  ~ifelse(is.infinite(.), NA, .)) %>%
  ungroup() %>%
  pivot_wider(names_from = Outcome, values_from = o_value, values_fn = mean) %>%
  pivot_wider(names_from = Trait, values_from = p_value, values_fn = mean) %>%
  group_by(study) %>% 
  mutate(n = n()) %>%
  select(-one_of(fctr_vars)) %>%
  distinct() %>%
  pivot_longer(cols = c(-study, -SID, -n), values_to = "value", names_to = "item", values_drop_na = T) %>%
  group_by(study, item, n) %>%
  summarize(est = sprintf("%.2f (%.2f)", mean(value, na.rm = T), sd(value, na.rm = T))) %>%
  ungroup() %>%
  pivot_wider(names_from = item, values_from = est) %>%
  full_join(
    nested_data %>% 
      group_by(Outcome, SID, study) %>%
      filter(o_year == min(o_year)) %>%
      ungroup() %>%
      select(-o_year) %>%
      pivot_wider(names_from = Outcome, values_from = o_value, values_fn = mean) %>%
      select(-Trait, -p_year, -p_value) %>% 
      distinct() %>%
      select(study, SID, one_of(fctr_vars)) %>% 
      distinct()  %>% 
      group_by(study) %>% 
      summarize_at(vars(-SID), ~mean(., na.rm = T)*100) %>% 
      mutate_at(vars(-study), ~ifelse(is.nan(.) | is.na(.), "", sprintf("%.2f%%", .))) %>%
      ungroup()
    ) %>%
    select(study, n, E, A, C, N, O, PA, `NA`, SWL, one_of(outcomes$short_name), 
           age, gender, education, cognition, BMI, SRhealth, smokes, alcohol, 
           BMI, race, stroke, cancer, diabetes, heartProb) %>% 
    transpose_df() %>%
  mutate(Variable = ifelse(Variable == "n", "Valid N", Variable)) %>% 
  mutate(Variable = mapvalues(Variable, c(traits$short_name, outcomes$short_name), str_wrap(c(traits$long_name, outcomes$long_name), 25))) %>%
  select(Variable, `Rush-MAP`, ROS, `WUSM-MAP`, EAS, GSOEP, HRS, LISS, SATSA) %>%
  kable(., "html"
        , digits = 2
        # , col.names = cln
        , caption = "<strong>Table 3</strong><br><em>Descriptive Statistics of All Harmonized Measures Across Samples"
        , align = c("l", rep("c",9))) %>%
    kable_classic(full_width = F, html_font = "Times New Roman") %>%
    kableExtra::group_rows("Big Five Personality", 2, 6) %>%
    kableExtra::group_rows("Subjective Well-Being", 7, 9) %>%
    kableExtra::group_rows("Dementia and Neuropathology", 10, 20) %>%
    kableExtra::group_rows("Covariates", 21, 33) %>%
  add_footnote(notation = "none", label = "<em>Note.</em> E = Extraversion; A = Agreeableness; C = Conscientiousness; N = Neuroticism; O = Openness, PA = Positive Affect, NA = Negative Affect, SWL = Satisfaction with Life; Age, education, gender, smoking, alcohol, BMI, chronic conditions, and cognition were assessed at the first baseline personality assessment.", escape = F); desc_tab
save_kable(desc_tab, file = sprintf("%s/results/tables/tab-3-desc.html", wd))
```

```{r}
nested_data %>% select(-Trait, -p_year, -p_value) %>% distinct()
```


```{r}
nested_data <- nested_data %>%
  group_by(Trait, Outcome, study, p_year) %>%
  mutate_at(vars(p_value, SRhealth),  ~((. - min(., na.rm = T))/(max(., na.rm = T) - min(., na.rm = T))*10)) %>%
  mutate_at(vars(p_value, SRhealth),  ~ifelse(is.infinite(.), NA, .)) %>%
  mutate(CC = rowSums(cbind(stroke, cancer, diabetes, heartProb), na.rm = T)) %>%
  mutate_at(vars(alcohol, smokes, stroke, cancer, diabetes, heartProb, gender), factor) %>%
  mutate(age = age - 60
         , education = education - 12) %>%
  ungroup()
nested_data
```


### Rescale Outcomes  
Now that we've got personality and covariates scaled, we will group by personality characteristic and outcome to rescale outcomes, as needed.  

```{r}
save_fun <- function(d, trait, outcome){
  if(outcome %in% c("dementia", "hipSclerosis", "lewyBodyDis", "tdp43", "vsclrInfrcts", "vsclrMcrInfrcts")){
    d <- d %>% mutate(o_value = factor(o_value))
  } 
  save(d, file = sprintf("%s/data/SCA/%s-%s.RData", wd, trait, outcome))
  return(d)
}

nested_data <- nested_data %>%
  group_by(Trait, Outcome) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = pmap(list(data, Trait, Outcome), save_fun))
nested_data 
```

### Bring in Moderators and Covariate Adjustments  
These full data sets will be used for sensitivity analyses and fully models, but we also want to set up our data for unadjusted models and moderator tests.  

```{r}
mod_setup_fun <- function(d, trait, outcome){
  crossing(Covariates = c("fully", "shared", "standard", "butOne", "unadjusted")
           , Moderator = c("none", "education", "age", "gender", "cognition")) %>%
    mutate(data = list(d)) %>%
    mutate(data = pmap(list(data, trait, outcome, Moderator, Covariates), mod_save_fun))
  return(NULL)
}

mod_save_fun <- function(d, trait, outcome, mod, cov){
  d2 <- if(cov == "unadjusted"){
    d %>% select(study, SID, p_year, p_value, o_year, o_value, one_of(mod)) %>% filter(complete.cases(.))
  } else if (cov == "shared"){
    d %>% select(study, SID, p_year, p_value, o_year, o_value, one_of(mod), age, gender, education, smokes, alcohol) %>% filter(complete.cases(.))
  } else if (cov == "standard"){
    d %>% select(study, SID, p_year, p_value, o_year, o_value, one_of(mod), age, gender, education) %>% filter(complete.cases(.))
  } else if (cov == "butOne") {
    d %>% select(study, SID, p_year, p_value, o_year, o_value, one_of(mod), age, gender, education, smokes, alcohol, cognition, CC) %>% filter(complete.cases(.))
  } else {
    d %>% filter(complete.cases(.))
  }
  # if(mod != "none") colnames(d2)[colnames(d2) == mod] <- "modvalue"
  save(d2, file = sprintf("%s/data/mega-analysis/%s/%s-%s-%s.RData"
                          , wd, cov, trait, outcome, mod))
  return(NULL)
}

nested_data %>%
  # filter(Outcome != "dementia") %>%
  mutate(data = pmap(list(data, Trait, Outcome), mod_setup_fun))
```

## Part 3: Models  
For these first models, we'll be testing three sets of covariates. For a full test of how covariates impact our inferences, we'll then follow up in a later step doing a specification curve / multiverse analysis.  

For these first models, we will run a series of Bayesian regressions. For binary outcomes, these will be multilevel logistic regressions, while for the others, these will be "regular" multilevel linear regressions. For each of these, we will also test age, gender, and education, and cognitive functioning as moderators.  

### Functions   
#### Model Function  

```{r}
ipd_mega_mod_fun <- function(trait, outcome, mod, cov){
  ## load the data
  load(sprintf("%s/data/mega-analysis/%s/%s-%s-%s.RData", wd, cov, trait, outcome, mod))
  
  ## compiled Bayesian model to speed up processing and avoid crashing
  if(outcome %in% c("dementia", "hipSclerosis", "lewyBodyDis", "tdp43", "vsclrInfrcts", "vsclrMcrInfrcts")) load(sprintf("%s/results/bayes_sample_mod_binomial.RData", wd)) else load(sprintf("%s/results/bayes_sample_mod_continuous.RData", wd))
  
  ## formula 
  cv <- c("age", "gender", "education", "smokes", "alcohol")
  #if (cov == "shared") cv <- cv
  if (cov == "butOne")  cv <- c(cv, "CC", "cognition")
  if (cov == "fully")    cv <- c(cv, "CC", "cognition", "BMI", "race", "SRhealth")
  if (cov == "standard") cv <- c("age", "gender", "education")
  rhs <- "p_value"
  rhs <- if(cov != "unadjusted") c(rhs, cv) else rhs
  if(mod != "none") rhs <- c(rhs, paste("p_value", mod, sep = "*"))
  re <- if(mod == "none") "(p_value | study)" else paste(paste("(p_value", mod, sep = " * "), "| study)")
  rhs <- paste(c(rhs, re), collapse = " + ")
  f <- paste("o_value ~ ", rhs, collapse = "")
  
  ## run the models & save
  m <- update(m
              , formula = f
              , newdata = d2
              , iter = 2000
              , warmup = 1000
              , cores = 4
              )
  save(m, file = sprintf("%s/results/models/%s/%s_%s_%s.RData"
                         , wd, cov, outcome, trait, mod))
  
  ## extract model terms and confidence intervals & save
  fx <- tidy(m, conf.int = T) %>%
    select(term, estimate, conf.low, conf.high)
  rx <- std_eff_fun(m)
  save(fx, rx, file = sprintf("%s/results/summary/%s/%s_%s_%s.RData"
                         , wd, cov, outcome, trait, mod))
  
  ## extract heterogeneity estimates
  het <- hetero_fun(m)
  save(het, file = sprintf("%s/results/heterogeneity/%s/%s_%s_%s.RData"
                         , wd, cov, outcome, trait, mod))
  
  ## simple effects for moderators
  if(mod != "none"){
    pred.fx <- fx_pred_fun(m, mod)
    pred.rx <- rx_pred_fun(m, mod)
    save(pred.fx, pred.rx, file = sprintf("%s/results/predicted/%s/%s_%s_%s.RData"
                         , wd, cov, outcome, trait, mod))
  }
  
  ## clean up the local function environment
  rm(list = c("d", "f", "rhs", "m", "fx", "rx", "het"))
  gc()
}
```

#### Study-Specific Effects Function  

As noted previously, once we run the model, we will have to use a second step to get the study-specific estimates for all studies. Unlike with dummy codes, doing so is much more straightforward. We just have to pull study-specific effects using the `coef()` for both Bayesian and Frequentist approaches.  

```{r study effects function}
std_eff_fun <- function(m){
    coef(m, probs = c(0.025, 0.975))[[1]] %>% array_tree(3) %>% 
      tibble(names = names(.), data = .) %>% 
      mutate(data = map(data, ~(.) %>% data.frame %>% 
        rownames_to_column("study"))) %>% 
      unnest(data) %>% 
      select(names, study, estimate = Estimate, conf.low = Q2.5, conf.high = Q97.5)
}
```

#### Heterogeneity Estimates Function   

The Final pieces of information we need to extract from these models are estimates of the heterogeneity of effects across studies.  

```{r heterogeneity function}
hetero_fun <- function(m){
  args <- list(x = m, effects = "ran_pars", conf.int = T)
  do.call(tidy, args) %>%
    select(group, term, estimate, conf.low, conf.high) %>%
    separate(term, c("est", "term"), sep = "__") %>%
    mutate_at(vars(estimate:conf.high), ~ifelse(est == "sd", .^2, .)) %>%
    mutate(est = ifelse(est == "sd", "var", est))
}
```

#### Simple Effects Function  
##### Fixed Effects  
```{r simple effects}
fx_pred_fun <-function(m, moder){
  d <- m$data 
  d <- d %>% select(-o_value, -p_value, -study)
  cols <- colnames(d)
  md_cl <- class(d[,moder])
  if(any(sapply(d, class) == "numeric")){
    msd <- d %>%
      select_if(is.numeric) %>%
      pivot_longer(everything()
                   , names_to = "item"
                   , values_to = "value") %>%
      group_by(item) %>%
      summarize_at(vars(value), lst(mean, sd)) %>%
      ungroup()
  }
  if(any(sapply(d, class) == "factor")){
    fct_lev <- d %>% 
      select_if(is.factor) %>%
      summarize_all(~list(levels(.)))
  }
  d <- d %>% select(-one_of(moder))
  
  md_levs <- if(md_cl == "numeric"){
    if(moder %in% c("age")) {
      c(-10, 0, 10)
      } else if (moder %in% c("education")) {
      c(-5, 0, 5) 
      } else {
        with(msd, c(mean[item == moder] - sd[item == moder], mean[item == moder], mean[item == moder] + sd[item == moder]))
      }
  } else { 
    sort(unique(fct_lev[,moder][[1]]))
  }
  
  md_fac <- if(moder == "age") c("-10 yrs", "60", "+10 yrs") else if (moder == "education") c("-5 yrs", "12 years", "+5 yrs") else if(moder == "gender") c("Male", "Female") else c("-1 SD", "M", "+1 SD")
  
  mod_frame <- expand.grid(
    p_value = seq(0,10,.1)
    , modvalue = md_levs
    , stringsAsFactors = F
    ) %>% 
    mutate(mod_fac = factor(modvalue, levels = unique(modvalue), labels = md_fac)) %>%
    setNames(c("p_value", moder, "mod_fac")) 
  
  if(ncol(d) > 0){
    if(any(sapply(d, class) == "numeric")){
      mod_frame <- tibble(mod_frame, d %>% select_if(is.numeric) %>% summarize_all(mean))
    } 
    if(any(sapply(d, class) == "factor")){
      fcts <- colnames(d)[sapply(d, class) == "factor"]
      for(i in 1:length(fcts)){
        fct <- fcts[i]
        mod_frame <- crossing(
          mod_frame
          , levels(d[,fct])
        ) %>% setNames(c(colnames(mod_frame), fct))
      }
    }
  }
  
  pred.fx <- 
    bind_cols(
      mod_frame, 
      fitted(m
             , newdata = mod_frame
             , re_formula = NA) %>% data.frame
    ) %>%
    select(one_of(colnames(m$data)), mod_fac, pred = Estimate, lower = Q2.5, upper = Q97.5) %>%
    group_by(p_value, mod_fac) %>% 
    summarize_at(vars(pred, lower, upper), mean) %>%
    ungroup()
  
  rm(list = c("m", "mod_frame", "d", "md_levs"))
  gc()
  return(pred.fx)
}
```

##### Study-Specific Effects  
```{r}
rx_pred_fun <- function(m, moder){
  d <- m$data
  d <- d %>% select(-o_value, -p_value)
  cols <- colnames(d)
  md_cl <- class(d[,moder])
  if(any(sapply(d, class) == "numeric")){
    msd <- d %>%
      group_by(study) %>%
      select_if(is.numeric) %>%
      pivot_longer(-study
                   , names_to = "item"
                   , values_to = "value") %>%
      group_by(study, item) %>%
      summarize_at(vars(value), lst(mean, sd), na.rm = T) %>%
      ungroup() 
  }
  if(any(sapply(d, class) == "factor")){
    fct_lev <- d %>% 
      group_by(study) %>%
      select_if(is.factor) %>%
      summarize_all(~list((levels(.)))) %>%
      ungroup()
  }
  d <- d %>% select(-one_of(moder))
  
  md_fac <- if(moder == "age") c("-10 yrs", "60", "+10 yrs") else if (moder == "education") c("-5 yrs", "12 years", "+5 yrs") else if(moder == "gender") c("Male", "Female") else c("-1 SD", "M", "+1 SD")
  
  md_levs <- if(moder != "cognition"){
    crossing(
      study = unique(d$study)
      , modvalue = if(moder == "age") c(-10, 0, 10) else if (moder == "education") c(-5,0,5) else c(0,1)
    ) %>%
      mutate(mod_fac = factor(modvalue, levels = unique(modvalue), labels = md_fac)) %>%
      setNames(c("study", moder, "mod_fac"))
  } else {
    msd %>% 
            filter(item == moder) %>%
            mutate(lower = mean - sd, upper = mean + sd) %>%
            select(-sd) %>% 
            pivot_longer(cols = c(mean, lower, upper)
                         , names_to = "meas"
                         , values_to = "modvalue") %>%
            pivot_wider(names_from = "item", values_from = "modvalue") %>%
            select(study, one_of(moder)) %>%
      setNames(c("study", "modvalue")) %>%
      group_by(study) %>%
      mutate(mod_fac = factor(modvalue, levels = unique(modvalue), labels = md_fac)) %>%
      ungroup() %>%
      setNames(c("study", moder, "mod_fac"))
  }
     
  mod_frame <- crossing(
      p_value = seq(0,10,.1)
      , md_levs
    )
  
  if(ncol(d) > 0){
    if(any(sapply(d, class) == "numeric")){
      mod_frame <- d %>% 
        group_by(study) %>% 
        select_if(is.numeric) %>% 
        summarize_all(mean, na.rm = T) %>%
        ungroup() %>%
        full_join(mod_frame)
    } 
    if(any(sapply(d, class) == "factor")){
      fcts <- colnames(d)[sapply(d, class) == "factor"]
      for(i in 1:length(fcts)){
        fct <- fcts[i]
        mod_frame <- crossing(
          mod_frame
          , levels(d[,fct])
        ) %>% setNames(c(colnames(mod_frame), fct))
      }
    }
  }
  
  pred.rx <- 
    bind_cols(
      mod_frame, 
      fitted(m
             , newdata = mod_frame) %>% data.frame
    ) %>%
    select(one_of(colnames(m$data)), mod_fac, pred = Estimate, lower = Q2.5, upper = Q97.5) %>%
    group_by(p_value, mod_fac, study) %>% 
    summarize_at(vars(pred, lower, upper), mean) %>%
    ungroup()
  
  rm(list = c("m", "mod_frame", "d"))
  gc()
  return(pred.rx)
}
```

### Run Models and Summaries  

```{r}
# Sample Bayesian Model 
# load data 
load(sprintf("%s/data/mega-analysis/shared/N-dementia-none.RData", wd))
# load("data/mega-analysis/shared/N-dementia-none.RData")

# clean data & keep only needed columns and a subset of the used variables
d <- d2 %>%
  group_by(study) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = map(data, ~(.) %>% filter(row_number() %in% sample(1:nrow(.), 100, replace = F)))) %>%
  unnest(data) 

# set priors & model specifications 
Prior <-  c(set_prior("cauchy(0,1)", class = "sd"),
            set_prior("student_t(3, 0, 2)", class = "b"),
            set_prior("student_t(3, 0, 5)", class = "Intercept"))
Iter <- 30; Warmup <- 21; treedepth <- 20
f <- formula(o_value ~ p_value + age + gender + education + (p_value | study))
m <- brm(formula = f
            , data = d
            , family = bernoulli(link = "logit")
            , prior = Prior
            , iter = Iter
            , warmup = Warmup
            , cores = 4)

save(m, file = sprintf("%s/results/bayes_sample_mod_binomial.RData", wd))
# save(m, file = "results/bayes_sample_mod_binomial.RData")

load(sprintf("%s/data/mega-analysis/shared/N-braak-none.RData", wd))
# load("data/mega-analysis/shared/N-braak-none.RData")

# clean data & keep only needed columns and a subset of the used variables
d <- d2 %>%
  group_by(study) %>%
  nest() %>%
  ungroup() %>%
  mutate(data = map(data, ~(.) %>% filter(row_number() %in% sample(1:nrow(.), 100, replace = T)))) %>%
  unnest(data) 

# set priors & model specifications 
Prior <-  c(set_prior("cauchy(0,1)", class = "sd"),
            set_prior("student_t(3, 0, 2)", class = "b"),
            set_prior("student_t(3, 0, 5)", class = "Intercept"))
Iter <- 30; Warmup <- 21; treedepth <- 20
f <- formula(o_value ~ p_value + age + gender + education + (p_value | study))
m <- brm(formula = f
            , data = d
            , prior = Prior
            , iter = Iter
            , warmup = Warmup
            , cores = 4)

save(m, file = sprintf("%s/results/bayes_sample_mod_continuous.RData", wd))
# save(m, file = "results/bayes_sample_mod_continuous.RData")
rm(list = c("d", "Prior", "Iter", "Warmup", "treedepth", "f", "m"))
```

```{r ipd reg run models}
done <- tibble(Covariate = c("fully", "shared", "butOne", "unadjusted", "standard"),
               file = map(Covariate, ~list.files(sprintf("%s/results/models/%s", wd, .)))) %>%
  unnest(file) %>%
  separate(file, c("Outcome", "Trait", "Moderator"), sep = "_") %>%
  mutate(Moderator = str_remove_all(Moderator, ".RData")
         , done = "done") %>%
  filter(!is.na(Moderator))

nested_ipd_mega <- crossing(
  Trait = traits$short_name
  , Outcome = outcomes$short_name
  , Moderator = c("education", "age", "gender", "cognition")
  , Covariate = c("fully", "shared", "butOne", "standard", "unadjusted")
) %>%
  full_join(
    crossing(
      Trait = traits$short_name
      , Outcome = outcomes$short_name
      , Moderator = "none"
      , Covariate = c("fully", "shared", "butOne", "standard", "unadjusted")
      )
) %>%
  # full_join(done) %>% filter((is.na(done) | Outcome == "dementia") & Covariate != "fully") %>%
  filter(Outcome == "dementia" & Covariate != "fully")
  mutate(run = pmap(list(Trait, Outcome, Moderator, Covariate), ipd_mega_mod_fun))

nested_ipd_mega %>% 
  mutate(Covariate = factor(Covariate)
         , Covariate = relevel(Covariate, "shared")
         , Moderator = factor(Moderator, levels = moders$short_name)) %>%
  arrange(Covariate, Outcome, Moderator, Trait) %>% 
  filter(Covariate != "fully") %>% 
  select(Trait, Outcome, Moderator, Covariate) %>%
  write.table(.
              , file = sprintf("%s/scripts/cluster/args/args.txt", wd)
              , row.names = F)
```

### DELETE LATER  
```{r}
# done <- tibble(type = c("Bayesian", "Frequentist"),
#                file = map(type, ~list.files(sprintf("%s/results/2a_ipd_dc/%s/predicted", wd, .)))) %>% 
#   unnest(file) %>%
#   separate(file, c("Outcome", "Trait", "Moderator", "Covariate"), sep = "_") %>%
#   mutate(Covariate = str_remove_all(Covariate, ".RData")
#          , done = "done") %>%
#   filter(!is.na(Covariate))

pred_fun <- function(file, outcome, trait, mod, cov){
  print(paste(cov, file))
  load(sprintf("%s/results/models/%s/%s_%s_%s.RData", wd, cov, outcome, trait, mod))
  fx <- tidy(m, conf.int = T) %>%
    select(term, estimate, conf.low, conf.high)
  rx <- std_eff_fun(m) 
  save(fx, rx, file = sprintf("%s/results/summary/%s/%s_%s_%s.RData"
                              , wd, cov, outcome, trait, mod))
  
  ## extract heterogeneity estimates
  het <- hetero_fun(m)
  save(het, file = sprintf("%s/results/heterogeneity/%s/%s_%s_%s.RData"
                         , wd, cov, outcome, trait, mod))
  
  if(mod != "none"){
    # load(sprintf("%s/results/models/%s/%s_%s_%s.RData", wd, cov, outcome, trait, mod))
    pred.fx <- fx_pred_fun(m, mod)
    pred.rx <- rx_pred_fun(m, mod)
    save(pred.fx, pred.rx, file = sprintf("%s/results/predicted/%s/%s_%s_%s.RData"
                          , wd, cov, outcome, trait, mod))
    rm(list = c("pred.fx", "pred.rx", "m"))
    gc()
    return(T)
  }
}

plan(multisession(workers = 6L))
tibble(Covariate = c("fully", "shared", "butOne", "standard", "unadjusted")) %>%
  mutate(file = map(Covariate, ~list.files(sprintf("%s/results/models/%s", wd, .)))) %>%
  unnest(file) %>%
  separate(file, c("Outcome", "Trait", "Moderator"), sep = "_", remove = F) %>% 
  mutate(Moderator = str_remove(Moderator, ".RData")) %>%
  filter(!is.na(Moderator)) %>%
  # left_join(done) %>% filter(is.na(done)) %>%
  # filter(((Trait %in% c("A", "E", "O") & Covariate == "all" & Moderator == "age") | 
  #        (Trait == "E" & Moderator == "education" & Covariate == "all") | 
  #        (Trait == "O" & Moderator == "age" & Covariate == "none"))
  #   & type != "Bayesian") %>%
  ## read in the files
  filter(Outcome == "dementia") %>%
  mutate(
    future_pmap(list(file, Outcome, Trait, Moderator, Covariate)
         # pmap(list(file, Outcome, Trait, Moderator, Covariate)
                     # , possibly(pred_fun, "uh oh")
         , pred_fun
                     , .options = furrr_options(
                       globals = c("traits", "moders"
                                   , "hetero_fun"
                                   ,"rx_pred_fun"
                                   , "std_eff_fun"
                                   , "fx_pred_fun"
                                   , "wd")
                       , packages = c("brms", "broom", "broom.mixed", "tidyverse")
                       )
                     , .progress = T
    ))
closeAllConnections()
```