--- 
title: "Personality Predictors of Dementia Diagnosis and Neuropathic Burden: A Mega-Analysis"
author: 
    
  - name        : Emorie D. Beck
    affiliation : University of California, Davis
  - name        : Tomiko Yoneda
    affiliation : Feinberg School of Medicine
  - name        : Daniel K. Mroczek
    affiliation : Feinberg School of Medicine, Northwestern University
  - name        : Eileen K. Graham
    affiliation : Feinberg School of Medicine
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\ %B %Y')`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
abstract: |
  | "INTRODUCTION: The extent to which the Big Five personality traits and subjective well-being (SWB) are discriminatory predictors of clinical manifestation of dementia versus dementia-related neuropathology is unclear."
  | "METHODS: Using data from eight independent studies (Ntotal=44,531; baseline Mage= years, % female), Bayesian multilevel models tested whether traits and SWB differentially predicted neuropsychological and neuropathological characteristics of dementia."
  | "RESULTS: Adjusting for sociodemographic and health covariates, synthesized and individual study results indicate that high neuroticism, low conscientiousness, and high negative affect were associated with increased risk of long-term dementia diagnosis."
  | "DISCUSSION: This multi-study project provides robust, conceptually replicated evidence that psychosocial factors are strong predictors of dementia diagnosis, but differentially associated with neuropathology at autopsy as a function of premorbid dementia diagnoses in some samples. These results suggest the possible importance of brain maintenance or test performance, while also highlighting the need for ongoing data collection efforts to disentangle these complex relationships."
link-citations: yes
github-repo: emoriebeck/personality-dementia-neuropath
description: "Personality, Dementia, and Neuropathology"
editor_options: 
  chunk_output_type: console
---

```{r, echo = F}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, error = F)
options(knitr.kable.NA = '')
```

# Workspace  

In this section, we'll set up everything we need to clean data in the next section. This includes: 

1. Loading in all packages
2. Loading in the codebook
  + Setting up data frames for personality traits / well-being, outcomes, covariates, and moderators, so that we can more easily rename their short-hand names to production ready ones later
3. Loading in and rendering html tables of some descriptives, measures, etc. 

## Packages  

First, let's load in the packages. Note the descriptions for each commented next to them.

```{r packages}
library(knitr)       # knit documents
library(kableExtra)  # formatted tables
library(readxl)      # read excel files
library(haven)       # read spss files
library(broom.mixed) # summaries of models
library(rstan)       # bayes underpinnings
library(tidybayes)   # pretty bayes draws and plots
library(cowplot)     # piece plots together
library(plyr)        # data wrangling
library(tidyverse)   # data wrangling
library(brms)        # bayesian models
library(furrr)       # parallel purrr mapping
library(psych)       # psychometrics
```

## Directory Path  

We have three different directories: 
1. `data_path` stores the raw that that cannot be shared per data use agreements
2. `res_path` includes the GitHub link where shareable objects can be found
3. `local_path` is mostly used to save files as they render, or in some limited cases of objects that hold raw data, to access those objects that can't be shared

```{r path}
data_path <- "/Volumes/Emorie/data"
# res_path <- "/Volumes/Emorie/projects/dementia/prediction"
res_path <- "https://github.com/emoriebeck/personality-dementia-neuropath/raw/master"
local_path <- "/Volumes/Emorie/projects/dementia/prediction"
```

## Codebook  

Each study has a separate codebook indexing covariate, moderator, personality, and outcome variables. Moreover, these codebooks contain information about the original scale of the variable, any recoding of the variable (including binarizing outcomes, changing the scale, and removing missing data), reverse coding of scale variables, categories, etc.  

```{r codebook}
# list of all codebook sheets
url <- "https://github.com/emoriebeck/personality-dementia-neuropath/raw/master/codebooks/master_codebook_09.04.20.xlsx?raw=true"
destfile <- "master_codebook_09.04.20.xlsx"
# destfile <- sprintf("%s/codebooks/%s", local_path, destfile)
curl::curl_download(url, destfile)
sheets <- excel_sheets(destfile)

# function for reading in sheets
read_fun <- function(x){
  read_xlsx(destfile, sheet = x)
}

# read in sheets and index source
codebook <- tibble(
  study = sheets,
  codebook = map(study, read_fun)
)

## short and long versions of names of all categories for later use
studies <-      c("ROS", "RADC-MAP", "EAS", "ADRC"    , "SATSA", "HRS", "LISS", "GSOEP")
studies_long <- c("ROS", "Rush-MAP", "EAS", "WUSM-MAP", "SATSA", "HRS", "LISS", "GSOEP")

stdcolors <- tibble(
  studies = c("Overall", studies)
  , studies_long = c("Overall", studies_long)
  , std_text = str_remove_all(studies, "[-]")
  , colors = c("black", "#332288", "#88ccee", "#44aa99", "#117733", "#999933", #"#ddcc77", "#cc6677", 
               "#332288", "#88ccee", "#44aa99")#, "#117733", "#999933", "#ddcc77")
       , lt = c(rep("solid", 6), rep("dotted", 3)))

traits <- codebook$codebook[[2]] %>% filter(category == "pers") %>% 
  select(long_name = Construct, short_name = name); traits

outcomes <- codebook$codebook[[2]] %>% filter(category == "out") %>%
  select(long_name = Construct, short_name = name, link, colnm); outcomes

moders <- codebook$codebook[[2]] %>% filter(category == "mod") %>%
  select(long_name = Construct, short_name = name, short_term = old_term, long_term = new_term); moders

covars <- codebook$codebook[[2]] %>% filter(category == "covariates") %>%
  select(long_name = Construct, short_name = name, desc = new_term); covars

# used personality waves 
url <- "https://github.com/emoriebeck/personality-dementia-neuropath/raw/master/codebooks/tables.xlsx?raw=true"
destfile <- "tables.xlsx"
# destfile <- sprintf("%s/codebooks/%s", local_path, destfile)
curl::curl_download(url, destfile)
p_waves <- read_xlsx(destfile, sheet = "Table 2")
```

## Tables   
### Table S1  

Below, I create Table S1, which includes information the personality and well-being scales used in each study:

```{r}
p_tab <- p_waves %>% 
  select(Study, everything(), -p_item, -Used) %>%
  filter(Study != "BLSA") %>%
  mutate(Measure = factor(Measure, traits$long_name)) %>%
  arrange(Study, Measure) 
rs <- p_tab %>% 
  group_by(Study) %>% 
  tally() %>% 
  mutate(end = cumsum(n), start = lag(end) + 1, start = ifelse(is.na(start), 1, start))
p_tab <- p_tab %>%
  select(-Study) %>%
  kable(.
        , "html"
        , caption = "<strong>Table S1</strong><br><em>Personality Trait and Subjective Well-Being Measurement Inventories, Scales, and Assessments Across Samples</em>"
        , escape = F
        , col.names = paste0("<strong>", colnames(p_tab)[-1], "</strong>")
        , align = c("r", "l", "l", "c")
        ) %>%
  kable_classic(full_width = F, html_font = "Times New Roman") 
for (i in 1:nrow(rs)){
  p_tab <- p_tab %>% kableExtra::group_rows(rs$Study[i], rs$start[i], rs$end[i])
}
p_tab
save_kable(p_tab, file = sprintf("%s/results/tables/tab-s1.html", local_path))
```

### Table S2  

Next, I create table S2, which indicates which measures were in each study, including which cognitive measures were in each sample. 

```{r}
meas <- read_xlsx(destfile, sheet = "Table 1") %>%
  select(-BLSA) 
rs <- meas %>% 
  group_by(Category) %>% 
  tally() %>% 
  mutate(end = cumsum(n), start = lag(end) + 1, start = ifelse(is.na(start), 1, start))
meas <- meas %>%
  select(-Category) %>%
  kable(.
        , "html"
        , caption = "<strong>Table S2</strong><br><em>List of Measures Across Samples</em>"
        , escape = F
        , col.names = paste0("<strong>", colnames(meas)[-1], "</strong>")
        , align = c("l", rep("c", 8))
        ) %>%
  kable_classic(full_width = F, html_font = "Times New Roman") 
for (i in 1:nrow(rs)){
  meas <- meas %>% kableExtra::group_rows(rs$Category[i], rs$start[i], rs$end[i])
}
meas
save_kable(meas, file = sprintf("%s/results/tables/tab-s2.html", local_path))
```

### Table S3  

Next, I create table S3, which indicates previous uses of the samples, their findings, and the distinction between them and the present study. 

```{r}
uses <- read_xlsx(destfile, sheet = "Table S3")
meas <- uses %>%
  kable(.
        , "html"
        , caption = "<strong>Table S3</strong><br><em>List of Prior Publications Examining Personality-Dementia or Neuropathology Associations</em>"
        , escape = F
        , col.names = paste0("<strong>", colnames(uses), "</strong>")
        , align = c("l", rep("c", 7), "l", "l")
        ) %>%
  kable_classic(full_width = F, html_font = "Times New Roman") 
meas
save_kable(meas, file = sprintf("%s/results/tables/tab-s3.html", local_path))
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


