--- 
title: "Personality Predictors of Dementia Diagnosis and Neuropathic Burden: A Mega-Analysis"
author: 
    
  - name        : Emorie D. Beck
    affiliation : Feinberg School of Medicine
  - name        : Daniel K. Mroczek
    affiliation : Feinberg School of Medicine, Northwestern University
  - name        : Eileen K. Graham
    affiliation : Feinberg School of Medicine
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\ %B %Y')`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
editor_options: 
  chunk_output_type: console
---

```{r, echo = F}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, error = F)
options(knitr.kable.NA = '')
```

# Workspace  
## Packages  

```{r packages}
library(knitr)       # knit documents
library(kableExtra)  # formatted tables
library(readxl)      # read excel files
library(haven)       # read spss files
library(broom.mixed) # summaries of models
library(rstan)       # bayes underpinnings
library(tidybayes)   # pretty bayes draws and plots
library(cowplot)
library(plyr)        # data wrangling
library(tidyverse)   # data wrangling
library(brms)        # bayesian models
library(furrr)       # parallel purrr mapping
library(psych)       # psychometrics
```

## Directory Path  
```{r path}
# res_path <- "https://github.com/emoriebeck/big-five-prediction/blob/master"
data_path <- "/Volumes/Emorie/data"
# res_path <- "~/Box/emorie post doc/01_projects/01_dementia/01_prediction"
res_path <- "/Volumes/Emorie/projects/dementia/prediction"
wd <- "/Volumes/Emorie/projects/dementia/prediction"
```

## Codebook  
Each study has a separate codebook indexing matching, covariate, personality, and outcome variables. Moreover, these codebooks contain information about the original scale of the variable, any recoding of the variable (including binarizing outcomes, changing the scale, and removing missing data), reverse coding of scale variables, categories, etc.  
```{r codebook}
# list of all codebook sheets
sheets <- sprintf("%s/codebooks/master_codebook_09.04.20.xlsx", res_path) %>% excel_sheets()

# function for reading in sheets
read_fun <- function(x){
  sprintf("%s/codebooks/master_codebook_09.04.20.xlsx", res_path) %>% read_xlsx(., sheet = x)
}

# read in sheets and index source
codebook <- tibble(
  study = sheets,
  codebook = map(study, read_fun)
)

## short and long versions of names of all categories for later use
studies <-      c("ROS", "RADC-MAP", "EAS", "ADRC"    , "SATSA", "HRS", "LISS", "GSOEP")
studies_long <- c("ROS", "Rush-MAP", "EAS", "WUSM-MAP", "SATSA", "HRS", "LISS", "GSOEP")

stdcolors <- tibble(
  studies = c("Overall", studies)
  , studies_long = c("Overall", studies_long)
  , std_text = str_remove_all(studies, "[-]")
  , colors = c("black", "#332288", "#88ccee", "#44aa99", "#117733", "#999933", #"#ddcc77", "#cc6677", 
               "#332288", "#88ccee", "#44aa99")#, "#117733", "#999933", "#ddcc77")
       , lt = c(rep("solid", 6), rep("dotted", 3)))

traits <- codebook$codebook[[2]] %>% filter(category == "pers") %>% 
  select(long_name = Construct, short_name = name)

outcomes <- codebook$codebook[[2]] %>% filter(category == "out") %>%
  select(long_name = Construct, short_name = name, link, colnm)

moders <- codebook$codebook[[2]] %>% filter(category == "mod") %>%
  select(long_name = Construct, short_name = name, short_term = old_term, long_term = new_term)

covars <- codebook$codebook[[2]] %>% filter(category == "covariates") %>%
  select(long_name = Construct, short_name = name, desc = new_term)

# used personality waves 
p_waves <- sprintf("%s/codebooks/tables.xlsx", res_path) %>% 
  read_xlsx(., sheet = "Table 2")
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


