---
title           : "Personality Predictors of Dementia Diagnosis and Neuropathic Burden: A Mega-Analysis"
shorttitle      : "Personality and Dementia"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\ %B %Y')`"

author: 
  - name        : Emorie D. Beck
    affiliation : Feinberg School of Medicine
  - name        : Daniel K. Mroczek
    affiliation : Feinberg School of Medicine, Northwestern University
  - name        : Eileen K. Graham
    affiliation : Feinberg School of Medicine

output: 
  html_document:
    theme: united
    highlight: tango
    df_print: paged
    code_folding: show
    toc: true
    toc_float: true
  
bibliography: r-references.bib
biblio-style: "apalike"
csl: "apa-6th-edition.csl"
---

```{r, echo = F, warning = F, message = F, results = 'hide'}
knitr::opts_chunk$set(echo = F, message = F, warning = F, error = F)
options(knitr.kable.NA = '')
library(knitr)
library(kableExtra)
library(plyr)
library(tidyverse)

wd <- "~/Box/emorie post doc/dementia/prediction"
```


# Study Information

## Title
<!-- Provide the working title of your study. It may be the same title that you submit for publication of your final manuscript, but it is not a requirement. The title should be a specific and informative description of a project. Vague titles such as 'Fruit fly preregistration plan' are not appropriate.

Example: Effect of sugar on brownie tastiness. -->

`r rmarkdown::metadata$title`


## Description
<!-- Please give a brief description of your study, including some background, the purpose of the of the study, or broad research questions. The description should be no longer than the length of an abstract. It can give some context for the proposed study, but great detail is not needed here for your preregistration.

Example: Though there is strong evidence to suggest that sugar affects taste preferences, the effect has never been demonstrated in brownies. Therefore, we will measure taste preference for four different levels of sugar concentration in a standard brownie recipe to determine if the effect exists in this pastry. -->

Personality traits are relatively stable, dispositional patterns that differentiate people from one another (Roberts, Wood, & Caspi, 2008). Personality traits are robust predictors of many life outcomes (Beck \& Jackson, 2020), including health outcomes such as disease diagnosis  [@weston2015personality], terminal cognitive decline [@wilson2015conscientiousness] and mortality risk [@mroczek2007personality; @graham2017personality]. They also are critical predictors of important factors that lead to later disease or early mortality, most notably health behaviors [@turiano2014perceived] and physician adherence [@hill2011role]. In fact, this is one mechanism by which psychological dimensions such as well-being or personality influence more distal health outcomes: via mediating factors such as lifestyle factors. Similar processes may operate with respect to post-dx cognitive decline among those with dementia. Those with particular personality- or well being-based predisposing factors, may have slower rates of decline, meaning less impairment and better functioning for a longer length of time even after the onset of dementia.  

## Research Question  
<!-- List specific, concise, and testable hypotheses. Please state if the hypotheses are directional or non-directional. If directional, state the direction. A predicted effect is also appropriate here. If a specific interaction or moderation is important to your research, you can list that as a separate hypothesis.

Example: If taste affects preference, then mean preference indices will be higher with higher concentrations of sugar. -->

1. Do personality and subjective well-being indicators (positive affect, negative affect, and satisfaction with life) predict dementia diagnosis?  

2. Do personality and subjective well-being indicators (positive affect, negative affect, and satisfaction with life) predict post-mortem levels of biomarkers and neurological pathology?  

## Hypotheses  
Previous research examining personality predictors of dementia diagnosis and neuropathic burden in single studies, including some of those used in the present study, will guide our expectations.  

**Hypothesis 1 -- Dementia Diagnoses:**  
A number of studies have investigated whether the Big Five prospectively predict dementia diagnoses. From these, we predict:  
- **Hypothesis 1A**: Conscientiousness will predict lower odds of dementia diagnoses [@wilson2007conscientiousness; @TERRACCIANO20131045; @terracciano2014personality; @duberstein2011personality].  
- **Hypothesis 1B**: Neuroticism will predict higher odds of dementia diganoses [@wilson2007conscientiousness; @terracciano2014personality; @duberstein2011personality].   
- **Hypothesis 1C**: Extraversion [@TERRACCIANO20131045; @terracciano2014personality] will not predict dementia diagnoses.  
- **Hypothesis 1D**: Results for Openness have been mixed, with Openness predicting lower odds of dementia diganoses in some [@duberstein2011personality] but not all [@terracciano2014personality] studies. Thus, we expect no association overall but coupled with cross-study heterogeneity.  
- **Hypothesis 1E**: Results for Agreeableness have been mixed, with Agreeableness predicting lower odds of dementia diganoses in some [Agreeableness @terracciano2014personality] but not all [Agreeableness, @duberstein2011personality] studies. Thus, we expect no association overall but coupled with cross-study heterogeneity.  

Although many investigations have examined well-being indicators following dementia diagnoses, very few have investigated whether well-being predicts who is diagnosed with dementia.  
- **Hypothesis 1F**: However, given Neuroticism's generally high positive low correlation with negative affect, we expect negative affect to predict higher odds of dementia diagnoses.  
- **Hypothesis 1G**: In addition, given Extraversion's modest association with positive affect, we expect positive affect to be unassociated with dementia dianoses.  
- **Hypothesis 1H:** Satisfaction with life will predict dementia diagnosis [@peitsch2016general].  

**Hypothesis 2 -- Neuropathic burden:**  
Few studies have examined the association between the Big Five and well-being indicators and neuropathic burden. As such, these results will be largely exploratory. However, based on the limited previous tests, we predict the following for Braak Stages, CERAD, tau protein, and amyloid beta levels:  
**Braak stages**: Neuroticism will predict more progression through Braak stages [@TERRACCIANO20131045], while Agreeableness will predict less progression [@TERRACCIANO20131045]. Negative Affect will likely predict Braak stages given its strong association with Neuroticism. The rest of the Big Five as well as satisfaction with life and postive affect will not be associated.  
**CERAD**: None of the Big Five will predict CERAD [@TERRACCIANO20131045].  
**tau-PET Protein**: Neuroticism (and, by extension, negative affect) will predict higher tau protein accumulation in several brain regions [@schultz2019association]. The rest of the Big Five as well as satisfaction with life and postive affect will not be associated.  
**$A\beta$**: Neuroticism (and, by extension, negative affect) will predict higher amyloid beta levels [@schultz2019association]. The rest of the Big Five as well as satisfaction with life and postive affect will not be associated.    


# Design Plan
<!-- In this section, you will be asked to describe the overall design of your study. Remember that this research plan is designed to register a single study, so if you have multiple experimental designs, please complete a separate preregistration. -->


## Study type

**Observational Study**. Data is collected from study subjects that are not randomly assigned to a treatment. This includes surveys, natural experiments, and regression discontinuity designs.  

## Study design
<!-- Describe your study design. Examples include two-group, factorial, randomized block, and repeated measures. Is it a between (unpaired), within-subject (paired), or mixed design? Describe any counterbalancing required. Typical study designs for observation studies include cohort, cross sectional, and case-control studies.

This question has a variety of possible answers. The key is for a researcher to be as detailed as is necessary given the specifics of their design. Be careful to determine if every parameter has been specified in the description of the study design. There may be some overlap between this question and the following questions. That is OK, as long as sufficient detail is given in one of the areas to provide all of the requested information. For example, if the study design describes a complete factorial, 2 X 3 design and the treatments and levels are specified previously, you do not have to repeat that information.

Example: We have a between subjects design with 1 factor (sugar by mass) with 4 levels. -->

The present study plans to use six existing longitudinal studies that include personality, dementia, cognitive ability, and background covariates. More detail on each study can be found below. Importantly, at the time of this preregistration, we are waiting for permission to use both the ADRC-MAP study and the BLSA study. This has two consequences. First, if access is not granted, we will not be able to include these studies. Second, until access is granted, we will not have access to the full data dictionaries, including variable names, scales, etc. However, the list of data requested are included in this preregistration and designed to match the those used in the ROSMAP, which will ensure consistent and reproducible data cleaning procedures.  

### Health and Retirement Study (HRS)  
The Health and Retirement Study [HRS; @juster1995overview] is an ongoing longitudinal study of households in the United States. These data are available at https://hrs.isr.umich.edu by creating a free account.  

Participants were recruited from more than 35,000 individuals from the financial households of individuals born between 1931 and 1941 in the US. Data have been collected biannually since 1992. The latest data release includes data up to 2016. On average, 10,000 individuals are sampled each wave More information on the HRS can be found at https://hrs.isr.umich.edu/documentation/survey-design, but, in short, the HRS is a nationally representative sample of adults over 50 in the US. It is critical to note that the HRS samples households of the original cohort and follows individuals and their spouses or partners until their death.  

Sample size varies by year, ranging from approximately 7,500 (2014) to 15,500 (1992). (https://hrs.isr.umich.edu/sites/default/files/biblio/ResponseRates_2017.pdf). This provides 99% power to detect a zero-order correlation effect size of ~.04, two-tailed at alpha .05.  

### RUSH Memory and and Aging Project (RUSH-MAP)  
The RUSH Memory and Aging Project (RUSH-MAP) is an ongoing longitudinal study that began in 1997 [@a2012overview]. These data are available, through application from https://www.radc.rush.edu/requests.htm.  

Participants who were 65 and older were recruited from retirement communities and subsidized senior housing facilities throughout Chicagoland and northeastern Illinois beginning in 1997. Data are collected annually, and all participants are organ donors. Additional participants are recuited each year. Additional information and documentation on the data can be found at https://www.radc.rush.edu/docs/var/variables.htm.  

Sample sizes vary by year, ranging from 52 (1997) to 2205 participants including 884 deceased participants with autopsy data (2019, 2020). This provides 99\% power to detect a zero-order correlation effect size of ~.10, two-tailed at alpha .05.  

### RUSH Religious Orders Study (ROS)  
The RUSH Religious Orders Study (ROS) is an ongoing longitudinal study that began in 1994 [@a2012overview]. These data are available, through application from https://www.radc.rush.edu/requests.htm. 

Older (65 and above) Catholic nuns, priests, and brothers with no prior dementia diagnosis and who agreed to annual evaluations and eventual organ donation were recruited from more than 40 groups across the United States. Additional participants are recuited each year. Additional information and documentation on the data can be found at https://www.radc.rush.edu/docs/var/variables.htm.  

Sample sizes vary bt year from 353 participants (1994) to 1487 participants, including 797 deceased participants with autopsy data (2019, 2020). This provides 99\% power to detect a zero-order correlation effect size of ~.11, two-tailed at alpha .05.  

### Swedish Adoption Twin Study of Aging (SATSA)  
The Swedish Adoption Twin Study of Aging (SATSA) is a longitudinal study of twin pairs from the Swedish Twin Registry that began in 1984. Data are available through the ICPSR database at https://www.icpsr.umich.edu/web/ICPSR/studies/3843.  

All twin-pairs on the Swedish Twin Registry who were separated at an early age were invited to be a part of the study in 1984. A control sample of twins reared together were also included. Additional waves of all participants were collected in 1987, 1990, 1993, 2004, 2007, 2010, 2012, and 2014. More information, including codebooks, scales, and variable search functions can be found at https://www.maelstrom-research.org/mica/individual-study/satsa/#.

Sample sizes vary by wave, ranging from 2018 participants at baseline (1984) to 379 participants (IPT7). Given that the target measures were collected at baseline, this provides 99\% power to detect a zero-order correlation effect size of ~.10, two-tailed at alpha .05. 

### ADRC Memory and Aging Project (ADRC-MAP)  
The Alzheimer Disease Research Center Memory and Aging Project (ADRC-MAP) is an ongoing longitudinal study of memory and Alzheimer's Disease that began in 1979. Data are available on a study-by-study basis through application from https://knightadrc.wustl.edu/Research/ResourceRequest.htm.

Participants were recruited from the Charles and Joanne F. Knight Alzheimer’s Disease Research Center at Washington University in St. Louis as part of an ongoing study of disease progression. The current study uses a subset of approximately 1200 of these participants who completed personality surveys as part of a substudy (see Duchek et al., 2019). More information on the study can be found at https://knightadrc.wustl.edu/Research/PDFs/Clinical%20Core%20list%20of%20measures.pdf.

Sample sizes vary over time, from approximately 400 to 1200. This provides 99% power to detect a zero-order correlation effect size of ~.15, two-tailed at alpha .05.  

### Baltimore Longitudinal Study of Aging (BLSA)  
The Baltimore Longitudinal Study of Aging (BLSA) is an ongoing longitudinal study of physical and psychological aging. The BLSA began in 1958 and has enrolled more than 3,200 participants to date, 1,300 of which are still active participants. Data are available on study-by-study basis through application at https://www.blsa.nih.gov/how-apply.  

Participants were recruited from the Baltimore area and brought into the BLSA for clinical evaluation every one to four years. Women were added to the study in 1978. The current study will use a subset of participants who completed at least one wave of personality. More information on the study can be found at https://www.nia.nih.gov/research/labs/blsa/about.

Sample sizes vary over time, with ranges across time not publically available. However, we suspect approximately 2,000 participants do have basic dementia diagnosis data and at least 700 to have autopsy data, which yields 99\% power to detect a zero-order correlation effect size of .10 and .16, respectively, two-tailed at alpha .05. 

# Sampling Plan
<!-- In this section we’ll ask you to describe how you plan to collect samples, as well as the number of samples you plan to collect and your rationale for this decision. Please keep in mind that the data described in this section should be the actual data used for analysis, so if you are using a subset of a larger dataset, please describe the subset that will actually be used in your study. -->


## Existing data
<!-- Preregistration is designed to make clear the distinction between confirmatory tests, specified prior to seeing the data, and exploratory analyses conducted after observing the data. Therefore, creating a research plan in which existing data will be used presents unique challenges. Please select the description that best describes your situation. Please do not hesitate to contact us if you have questions about how to answer this question (prereg@cos.io). -->

**Registration prior to accessing the data**. As of the date of submission, the data exist, but have not been accessed by you or your collaborators. Commonly, this includes data that has been collected by another researcher or institution.

**Registration prior to analysis of the data**. As of the date of submission, the data exist and you have accessed it, though no analysis has been conducted related to the research plan (including calculation of summary statistics). A common situation for this scenario when a large dataset exists that is used for many different studies over time, or when a data set is randomly split into a sample for exploratory analyses, and the other section of data is reserved for later confirmatory data analysis.

## Explanation of existing data
<!-- If you indicate that you will be using some data that already exist in this study, please describe the steps you have taken to assure that you are unaware of any patterns or summary statistics in the data. This may include an explanation of how access to the data has been limited, who has observed the data, or how you have avoided observing any analysis of the specific data you will use in your study.

An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results. After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point.

Example: An appropriate instance of using existing data would be collecting a sample size much larger than is required for the study, using a small portion of it to conduct exploratory analysis, and then registering one particular analysis that showed promising results. After registration, conduct the specified analysis on that part of the dataset that had not been investigated by the researcher up to that point. -->

The first author, who will be conducting all analyses, has previously worked with data from the Health and Retirement Study, including key personality data. However, she has not previously worked with dementia data from HRS. She has not previously worked with or accessed RUSH-MAP, ROS, ADRC-MAP, SATSA, and BLSA data. All core variables, data cleaning procedures, and analytic procedures for each of these studies are included with the present preregistration, where possible.  

## Sample size rationale
<!-- This could include a power analysis or an arbitrary constraint such as time, money, or personnel. This gives you an opportunity to specifically state how the sample size will be determined. A wide range of possible answers is acceptable; remember that transparency is more important than principled justifications. If you state any reason for a sample size upfront, it is better than stating no reason and leaving the reader to "fill in the blanks." Acceptable rationales include: a power analysis, an arbitrary number of subjects, or a number based on time or monetary constraints.

Example: We used the software program G*Power to conduct a power analysis. Our goal was to obtain .95 power to detect a medium effect size of .25 at the standard .05 alpha error probability. -->

Sample sizes vary across study and waves (see above). But each of these studies have at least 1000 participants, which provides 99% power to detect correlations of at least .14, two-tailed alpha at .05. And overall estimates will have considerably higher power.  


## Stopping rule
<!-- If your data collection procedures do not give you full control over your exact sample size, specify how you will decide when to terminate your data collection. 

You may specify a stopping rule based on p-values only in the specific case of sequential analyses with pre-specified checkpoints, alphas levels, and stopping rules. Unacceptable rationales include stopping based on p-values if checkpoints and stopping rules are not specified. If you have control over your sample size, then including a stopping rule is not necessary, though it must be clear in this question or a previous question how an exact sample size is attained.

Example: We will post participant sign-up slots by week on the preceding Friday night, with 20 spots posted per week. We will post 20 new slots each week if, on that Friday night, we are below 320 participants. -->

The authors did not collect these data and most of these studies are still enrolling participants. Sample sizes will be determined by data sent to the authors shortly after preregistration.  

# Variables
<!-- In this section you can describe all variables (both manipulated and measured variables) that will later be used in your confirmatory analysis plan. In your analysis plan, you will have the opportunity to describe how each variable will be used. If you have variables which you are measuring for exploratory analyses, you are not required to list them, though you are permitted to do so. -->


## Measured variables
<!-- Describe each variable that you will measure. This will include outcome measures, as well as any predictors or covariates that you will measure. You do not need to include any variables that you plan on collecting if they are not going to be included in the confirmatory analyses of this study.

Observational studies and meta-analyses will include only measured variables. As with the previous questions, the answers here must be precise. For example, 'intelligence,' 'accuracy,' 'aggression,' and 'color' are too vague. Acceptable alternatives could be 'IQ as measured by Wechsler Adult Intelligence Scale' 'percent correct,' 'number of threat displays,' and 'percent reflectance at 400 nm.'

Example: The single outcome variable will be the perceived tastiness of the single brownie each participant will eat. We will measure this by asking participants ‘How much did you enjoy eating the brownie’ (on a scale of 1-7, 1 being 'not at all', 7 being 'a great deal') and 'How good did the brownie taste' (on a scale of 1-7, 1 being 'very bad', 7 being 'very good'). -->

There will three categories of data:  

**(1) Personality** will be measured using Big Five Personality scales.  **Well-being measures** will be separate measures of positive affect, negative affect, and satisfaction with life separately, as available in each study.  

**(2) Dementia markers** will be measured using clinical diagnoses and post-mortem neuropathic indicators. Cognitive and physical symptom dementia diagnoses will be measured using self-report diagnoses, CDR's, and clinician diagnoses. 

Post-mortem dementia diagnoses and severity will be measured using a subset of vascular, neuropathological, cerebrospinal, and imaging indices, may of which are based on the National Alzheimer's Coordinating Center's Neuropathology Data Form:  
- Braak stage (0 to 6)  
- CERAD (1 = definite to 4 = no AD)  
- Overall Amyloid Beta Score (average cross-region percent area of cortex oocupied by amyloid beta)  
- Diffuse plaque burden (average of scaled regional counts)  
- Neuritic plaque burden (average of scaled regional counts)  
- Neuronal neurofibrillary tangle density (mean density across regions per $mm^2$)  
- Neuronal neurofibrillary tangle burden (average of scaled regional counts)  
- Lewy Body Disease  (4 level; 0 = none, 1 = nigral-predominant; 2 = limbic-type; 3 = neocortical-type)  
- Gross Cerebral Infarcts (0 = No, 1 = Yes)  
- Gross Cerebral Microinfarcts (0 = No, 1 = Yes)  
- Cerebral Atherosclerosis (0 = none to 3 = severe)  
- Cerebral Amyloid Angiopathy (0 = none to 3 = severe)  
- Arteriolosclerosis (0 = none to 3 = severe)  
- Hippocampal Sclerosis (0 = No, 1 = Yes)  
- Total CSF tau  
- Human protein tau 181  
- CSF $A\beta_{42}$ (Amyloid Beta Protein)  

<!-- (3) Cognitive Ability (and decline) will be measured using sets of tests specific to each study, many of which are drawn from the Wechsler Adult Intelligence Scale.   -->

**(3) Background variables**: 
- age (numeric)  
- gender (0 = male, 1 = female)
- race (0 = white, 1 = Black, 2 = other)  
- education (0 = high school or below; 1 = college, 2 = higher degree)  
- cognitive ability (scored within study, operationalized at POMP)  
- marital status (0 = not married, 1 = married)  
- self-rated health (scored within study on Likert-like scales, operationalized as POMP)
- heart problems (0 = no, 1 = yes)  
- stroke (0 = no, 1 = yes)  
- diabetes (0 = no, 1 = yes)  
- cancer (0 = no, 1 = yes)  
- respiratory disorders (0 = no, 1 = yes)  
- smoking (0 = no, 1 = yes)  
- alcohol (scored within study on Likert-like scales or days/week, operationalized as POMP)  

A summary of the personality variables are in Table 1, and which measures were available in each study are in Table 2.  

```{r}
sprintf("%s/codebooks/tables.xlsx", wd) %>%
  readxl::read_xlsx(., sheet = "Table 2") %>%
  select(-Measure) %>%
  kable(.
        , "html"
        , caption = "<strong>Table 1</strong><br><em>Personality and Well-Being Measures and Scales Across Studies</em>") %>%
  kable_styling(full_width = F) %>%
  kableExtra::group_rows("Extraversion", 1, 7) %>%
  kableExtra::group_rows("Agreeableness", 8, 14) %>%
  kableExtra::group_rows("Conscientiousness", 15, 21) %>%
  kableExtra::group_rows("Neuroticism", 22, 28) %>%
  kableExtra::group_rows("Openness", 29, 35) %>%
  kableExtra::group_rows("Satisfaction with Life", 36, 42) %>%
  kableExtra::group_rows("Positive Affect", 43, 49) %>%
  kableExtra::group_rows("Negative Affect", 50, 56)
```

```{r}
sprintf("%s/codebooks/tables.xlsx", wd) %>%
  readxl::read_xlsx(., sheet = "Table 1") %>%
  select(-Category) %>%
  kable(.
        , "html"
        , align = c("r", rep("c", 8))
        , caption = "<strong>Table 2</strong><br><em>Personality, Well-Being, Dementia, and Cognition Measures Across Studies</em>") %>%
  kable_styling(full_width = F) %>%
  kableExtra::group_rows("Personality and Well-Being", 1, 8) %>%
  kableExtra::group_rows("Dementia Diagnoses and Markers", 9, 26) %>%
  kableExtra::group_rows("Cognitive Tests", 27, 42) %>%
  kableExtra::group_rows("Background Covariates", 43, 56)
```

More detail on the scale, recoding, and summarizing of these data are available in the codebook attached with this preregistration.  


## Indices
<!-- If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined? Include either a formula or a precise description of your method. If your are using a more complicated statistical method to combine measures (e.g. a factor analysis), you can note that here but describe the exact method in the analysis plan section.

If you are using multiple pieces of data to construct a single variable, how will this occur? Both the data that are included and the formula or weights for each measure must be specified. Standard summary statistics, such as "means" do not require a formula, though more complicated indices require either the exact formula or, if it is an established index in the field, the index must be unambiguously defined. For example, "biodiversity index" is too broad, whereas "Shannon’s biodiversity index" is appropriate.

Example: We will take the mean of the two questions above to create a single measure of 'brownie enjoyment.'  -->

Personality and well-being measures will be composited into trait scores preserving the original scale in each data set. Then, personality scores in each data set will be converted to Percentages Of the Maximum Possible score (POMP) in the mega-analytic procedure [@cohen1999problem]. Unlike standardization procedures, that have a mean of zero and unit variance and can be misleading when data are skewed, POMP does not rescale sample variance based on the observed data, which overly relies on deviations from the mean. Instead, POMP relies on the ratio between the difference between a score and the minimum and the maximum and minimum, or  

POMP = $\frac{observed-minimum}{maximum-minimum}$*10.  

More information on the exact scales used to create the variables are in the table below.  

# Analysis Plan
<!-- You may describe one or more confirmatory analysis in this preregistration. Please remember that all analyses specified below must be reported in the final article, and any additional analyses must be noted as exploratory or hypothesis generating.

A confirmatory analysis plan must state up front which variables are predictors (independent) and which are the outcomes (dependent), otherwise it is an exploratory analysis. You are allowed to describe any exploratory work here, but a clear confirmatory analysis is required. -->

The analysis plan will be broken into parts to answer different questions associated with this study.  

Following pre-registration of this study, all data will be downloaded from study websites or received directly from data maintainers for each study. All target variables, as well as their rescaling and cleaning procedures, have been preregistered with this study.  

After all data are received, data for each study will be cleaned separately by the first author. These cleaning procedures can be roughly broken into pulling, rescaling, and/or compositing (1) background variables at baseline, (2) baseline personality and well-being (henceforth, baseline personality), (3) self-reported or clinician dementia diagnoses, (4) biomarkers of post-mortem dementia.  

Once each data set is prepared, data sets across studies will be combined and scales will be harmonized as needed (e.g., POMP for personality data will be calculated separately for each test due to differences in data missingness across models).  

Once data are combined, we will address the two main research questions, both of which will use the `brms` package in `R`.  

**1. Do personality and subjective well-being indicators (positive affect, negative affect, and satisfaction with life) predict dementia diagnosis?**  

First, to test whether personality predicts dementia diagnosis, we will run two separate models because diagnosis is a categorical (0 = no diagnosis, 1 = diagnosis) while biomarkers are continuous.

For diagnoses, we will run a series of bayesian multilevel logistic regression models, while for biomarkers we will run a series of bayesian multiple regression models. For both the basic model equation is the same: 

**Level 1**: $Y_{ij}= \beta_{0j}+ \beta_{1j}\ast P_{ij}+ \varepsilon_{ij}$  
**Level 2**:  
	- $\beta_{0j}= \gamma_{00} + u_{0j}$  
	- $\beta_{1j}= \gamma_{10} + u_{1j}$,  
	
For the logistic regressions, $\gamma_{00}$ is the average log odds of experiencing the outcome across all studies and $\gamma_{10}$ multiple of log odds change associated with a one-unit change in the percentage of the maximum of the possible (POMP) personality score. All results will be presented both as log odds and as odds ratios (OR) with 95\% credibility intervals (CI). $u_{0j}$ indicates the difference between the average estimate of log odds of experiencing an outcome and the estimate for each study (i.e. the study-specific estimate  of the log odds of each outcome), and $u_{1j}$ indicates the difference between the average multiple of log odds associated with a one unit change in POMP personality score and the estimate for each study (i.e. the study-specific estimate of the personality-outcome relationship). Each of these will be presented as forest plots showing both study-specific and average effects.  

**2. Do personality and subjective well-being indicators (positive affect, negative affect, and satisfaction with life) predict post-mortem levels of biomarkers and neurological pathology?**  

For the regressions predicting biomarkers from personality, the models will vary depending on whether the outcome is continuous or nominal. Some outcomes, like the presence of gross cerebral infarcts, are dichotomous, so the models will be logistic as with dementia diagnoses. However, others, like neuronal neurofibrillary tangle burden, are continuous such that there should be no need to transform the outcome variable (i.e. no logit link needed). For nominal outcomes, the interpretation of model parameters is the same as for dementia diagnoses. However, for continuous outcomes, $\gamma_{00}$ is the average level of each biomarker across all studies and $\gamma_{10}$ change in each biomarker associated with a one-unit change in the percentage of the maximum of the possible (POMP) personality score. All results will be presented as unstandardized regression coefficients with 95\% credibility intervals (CI). $u_{0j}$ indicates the difference between the average estimate of biomarker levels and the estimate for each study (i.e. the study-specific estimate average biomarker levels), and $u_{1j}$ indicates the difference between the average biomarker levels associated with a one unit change in POMP personality score and the estimate for each study (i.e. the study-specific estimate of the personality-biomarker relationship). Each of these will be presented as forest plots showing both study-specific and average effects.  

<!-- 2. Do personality and subjective well-being indicators (positive affect, negative affect, and satisfaction with life) predict disease progression among those diagnosed with dementia?   -->

<!-- Next, we will examine whether personality predicts decline following diagnoses. To do this, we will create two separate sub-samples for each study, one based on clinical diagnoses and one based on autopsy diagnoses. Next, we will estimate slopes of cognitive variables and test whether personality moderates the these trajectories.   -->

<!-- To do so, we will estimate a series of Bayesian cross-classified random slope piecewise multilevel models. The cross-classified random slope model is an extension of the basic piecewise growth model typically used in examination of socialization effects below:  -->

<!-- Level 1: $Y_{ij} = \beta_{0j} + \beta_{1j}*prewave_{ij} + \beta_{2j}*postwave_{ij} + \epsilon_{ij}$   -->
<!-- Level 2:   -->
<!-- - $\beta_{0j} = \gamma_{00} + \gamma_{01}*personality_{j} + u_{0j}$   -->
<!-- - $\beta_{1j} = \gamma_{10} + \gamma_{11}*personality_{j} + u_{1j}$   -->
<!-- - $\beta_{1j} = \gamma_{20} + \gamma_{21}*personality_{j} + u_{2j}$   -->

<!-- where $\gamma_{00}$ is the average cognitive ability score of those with the lowest score in each personality measure at baseline, $\gamma_{01}$ is the average difference in baseline cognitive ability associated with a one unit increase in personality, $\gamma_{10}$ is the average slope of cognitive ability change of those with the lowest score in each personality measure at baseline, and $\gamma_{11}$ is the change in average slope of cognitive ability associated with a one unit change in personality. Most critically, however, are the post-dementia coefficients, $\gamma_{20}$ and $\gamma_{21}$, which capture the difference between pre- and post-event levels and change. Specifically, $\gamma_{20}$ is the difference between pre- and post-dementia average cognitive ability change among those iwth the lowester score in each personailty measure at baseline, and $\gamma_{21}$ is the difference in pre-post trajectory change associated with a one unit change in personality. $u_{0j}$ captures the difference between the overall average baseline cognitive ability score and an individual's score, $u_{1j}$ captures the differences between the overall average cognitive ability change and an individual's change, and $u_{2j}$ captures individuals' deviations from teh difference in pre-post trajectory change.   -->

<!-- The cross-classified random slope model extends this by added a second, non-hierarchical random intercept and slope to the basic socialization growth model as below:  -->

<!-- Level 1: $Y_{ij} = \beta_{0j} + \beta_{1j}*prewave_{ij} + \beta_{2j}*postwave_{ij} + \epsilon_{ij}$   -->
<!-- Level 2:   -->
<!-- - $\beta_{0j} = \gamma_{00} + \gamma_{01}*Personality_{j} + u_{0j, study} + u_{0j, sid}$   -->
<!-- - $\beta_{1j} = \gamma_{10} + \gamma_{11}*Personality_{j} + u_{1j, study} + u_{1j, sid}$   -->
<!-- - $\beta_{2j} = \gamma_{20} + \gamma_{21}*Personality_{j} + u_{2j, study} + u_{2j, sid}$ -->

<!-- The notation here has been somewhat forced into a framework that matches the basic growth model for ease of interpretation. But essentially, it estimates cross-classified random effects for each study-person combination. These are independent in the sense that they are necessarily uncorrelated.  Given these effects, we can estimate and report study-specific and person-specific intercepts, group differences in intercepts, slopes, and cross-level interactions between personality and cognitive ability change (i.e. does personality predict change).   -->

All results will be presented both as unstandardized estimates (in terms of POMP) with 95\% credibility intervals (CI). Each effect will be presented as forest plots showing both study-specific and average effects or spaghetti plots showing person-specific effects.

## Statistical models
<!-- What statistical model will you use to test each hypothesis? Please include the type of model (e.g. ANOVA, multiple regression, SEM, etc) and the specification of the model (this includes each variable that will be included as predictors, outcomes, or covariates). Please specify any interactions, subgroup analyses, pairwise or complex contrasts, or follow-up tests from omnibus tests. If you plan on using any positive controls, negative controls, or manipulation checks you may mention that here. Remember that any test not included here must be noted as an exploratory test in your final article.

This is perhaps the most important and most complicated question within the preregistration. As with all of the other questions, the key is to provide a specific recipe for analyzing the collected data. Ask yourself: is enough detail provided to run the same analysis again with the information provided by the user? Be aware for instances where the statistical models appear specific, but actually leave openings for the precise test. See the following examples:

- If someone specifies a 2x3 ANOVA with both factors within subjects, there is still flexibility with the various types of ANOVAs that could be run. Either a repeated measures ANOVA (RMANOVA) or a multivariate ANOVA (MANOVA) could be used for that design, which are two different tests. 
- If you are going to perform a sequential analysis and check after 50, 100, and 150 samples, you must also specify the p-values you’ll test against at those three points.

Example:  We will use a one-way between subjects ANOVA to analyze our results. The manipulated, categorical independent variable is 'sugar' whereas the dependent variable is our taste index. -->

Statistical models will be Bayesian Multilevel Models. For dichotomous outcomes, we will use a logit link.  

Models will be run separately for each trait-outcome combination, both with and without background variables / covariates, but interpreted results will include all covariates. Unadjusted models will be included in Supplementary Materials. However, given the relative rarety of some markers (e.g., Lewy Body Disease), some trait-outcome associations will be dropped on a case-by case basis when at least two studies have less than 50 individuals with a diagnosis.  

## Transformations
<!-- If you plan on transforming, centering, recoding the data, or will require a coding scheme for categorical variables, please describe that process. If any categorical predictors are included in a regression, indicate how those variables will be coded (e.g. dummy coding, summation coding, etc.) and what the reference category will be.

Example: The "Effect of sugar on brownie tastiness" does not require any additional transformations. However, if it were using a regression analysis and each level of sweet had been categorically described (e.g. not sweet, somewhat sweet, sweet, and very sweet), 'sweet' could be dummy coded with 'not sweet' as the reference category. -->

All data recoding, compositing, and transformations are meticulously documented in the codebook attached with this preregistration. This codebook will be directly read into `R` for the purposes of rescaling and recoding variables to ensure maximal transparency and reproducibility.  

Key transformations are:  
- Personality, well-being, self-rated health, and cognitive ability will be scaled as POMP across studies.  
- Education will be coded as 0 = high school or below, 1 = college, and 2 = higher degree  
- Gender will be coded as 0 = male, 1 = female  

## Inference criteria
<!-- What criteria will you use to make inferences? Please describe the information youÍll use (e.g. p-values, bayes factors, specific model fit indices), as well as cut-off criterion, where appropriate. Will you be using one or two tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, will you account for this?

p-values, confidence intervals, and effect sizes are standard means for making an inference, and any level is acceptable, though some criteria must be specified in this or previous fields. Bayesian analyses should specify a Bayes factor or a credible interval. If you are selecting models, then how will you determine the relative quality of each? In regards to multiple comparisons, this is a question with few "wrong" answers. In other words, transparency is more important than any specific method of controlling the false discovery rate or false error rate. One may state an intention to report all tests conducted or one may conduct a specific correction procedure; either strategy is acceptable.

Example: We will use the standard p<.05 criteria for determining if the ANOVA and the post hoc test suggest that the results are significantly different from those expected if the null hypothesis were correct. The post-hoc Tukey-Kramer test adjusts for multiple comparisons. -->

Inference tests will all be based around the Bayesian 95\% credibility interval (CI) of the effect. Intervals that do not overlap with 0 will be considered statistically significant.  

## Data exclusion and missing data  
<!-- How will you determine what data or samples, if any, to exclude from your analyses? How will outliers be handled? Will you use any awareness check? Any rule for excluding a particular set of data is acceptable. One may describe rules for excluding a participant or for identifying outlier data.

Example: No checks will be performed to determine eligibility for inclusion besides verification that each subject answered each of the three tastiness indices. Outliers will be included in the analysis. -->

Every effort will be made to use the maximum amount of data possible. However, participants who are missing key personality, well-being, dementia diagnosis, biomarkers, cognitive ability scores, or demographic variables will be dropped in analyses involving those variables. Where possible, they will still be included in other tests.  

Participants who have no record of any personality characteristic or dementia diagnosis (positive or negative) be dropped completely.  

No imputation will be used.  

## Exploratory analyses (optional)
<!-- If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here. An exploratory test is any test where a prediction is not made up front, or there are multiple possible tests that you are going to use. A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could be registered at a later time.

Example: We expect that certain demographic traits may be related to taste preferences. Therefore, we will look for relationships between demographic variables (age, gender, income, and marital status) and the primary outcome measures of taste preferences. -->

We will examine four moderators of personality predicting dementia diagnosis and status: age (in years, centered within-study), gender, education (in years, centered at 12, i.e. high school), and baseline cognitive ability (scaled as POMP).  

# References
```{r create_r-references}
papaja::r_refs(file = "r-references.bib")
```

